---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readflexfile

<!-- badges: start -->
[![technomics: costverse](https://img.shields.io/badge/technomics-costverse-EAC435.svg)](https://github.com/technomics)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![R build status](https://github.com/Technomics/readflexfile/workflows/R-CMD-check/badge.svg)](https://github.com/Technomics/readflexfile/actions)
[![coverage: 1.7%25](https://img.shields.io/badge/coverage-1.7%25-red.svg)](https://cran.r-project.org/web/packages/covr/vignettes/how_it_works.html)
[![version: 0.2.0](https://img.shields.io/badge/version-0.2.0-blue.svg)]()
<!-- badges: end -->

The goal of readflexfile is to facilitate the reading of the FlexFile from the original JSON format into R. The package also includes helpful functions to flatten the schema into a single table.

View the [package site](https://technomics.github.io/readflexfile) to explore the features!

If you find a bug or have an idea for a new feature, please use the [issue board](https://github.com/Technomics/readflexfile/issues).

## Welcome to the costverse!

The *costverse* is a collection of R packages, inspired by the *tidyverse*. The goal is to create a cohesive ecosystem of R packages to streamline tasks encountered by analysts in the cost analysis profession. This can range from importing common data formats, working with difficult data structures (e.g., a WBS), or applying more advanced analytical techniques!

The *costverse* began as an internal [Technomics](https://www.technomics.net/) project to develop a set of tools that enable our employee owners to solve our clients’ problems more effectively. While aspects of the project remain internal, the following packages are currently available to the public. You are free to use them under the [GPLv3](https://www.gnu.org/licenses/gpl-3.0.en.html) - all that we ask is to please cite us as the authors.

 - [costmisc](https://github.com/Technomics/costmisc/)
 - [readflexfile](https://github.com/Technomics/readflexfile/)
 - [flexample](https://github.com/Technomics/flexample/)
 
Do not hesitate to contact us if you have questions about what else is in the works!

## Installation

You can download and install directly from our GitHub repository. If this does not work or does not have a build for your version of R, try using `install_github()` instead (see Development version instructions).

```{r eval=FALSE}
install.packages("flexample", repos = "https://technomics.github.io/repo/")
```

### Development version

To get a bug fix, or to use a feature from the development version, you can install readflexfile using the following. 

```{r eval=FALSE}
devtools::dev_mode(on = TRUE)
devtools::install_github("Technomics/readflexfile")
```
