---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readflexfile

<!-- badges: start -->
[![technomics: costverse](https://img.shields.io/badge/technomics-costverse-EAC435.svg)](https://gitlab.technomics.net/costverse)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Build: passing](https://img.shields.io/badge/build-passing-green.svg)](https://gitlab.technomics.net/costverse/readflexfile.git)
[![coverage: 0%25](https://img.shields.io/badge/coverage-0%25-blue.svg)]()
[![technomics: proprietary](https://img.shields.io/badge/technomics-proprietary-00A0B2.svg)](https://gitlab.technomics.net/)
[![version: 0.1.1](https://img.shields.io/badge/version-0.1.1-blue.svg)]()
<!-- badges: end -->

The goal of readflexfile is to facilitate the reading of the FlexFile from the original JSON format into R. The package also includes helpful functions to flatten the schema into a single table.

View the [package site](http://shiny.technomics.net/tran/www/docs/readflexfile).

## Installation

You can install the released version of readflexfile from [TRAN](http://shiny.technomics.net/tran/www/home/) with:

```{r eval=FALSE}
install.packages("readflexfile", repos = "http://shiny.technomics.net/tran")
```

### Development version

To get a bug fix, or to use a feature from the development version, you can install readflexfile from GitLab using [`rnomics`](http://shiny.technomics.net/tran/www/docs/rnomics/).

```{r eval=FALSE}
rnomics::gitlab_install("costverse/readflexfile", branch = "master")
```

### Clone Repository

Clone the repository into a working directory of your choice. Use either the RStudio menus or [`rnomics`](http://shiny.technomics.net/tran/www/docs/rnomics/).

```{r eval=FALSE}
rnomics::gitlab_clone("costverse/readflexfile", "your/file/directory/here")
```
